---
title: "Simple Graphs in R"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(devtools)
library(tidyverse)
library(WILD7150)
knitr::opts_chunk$set(echo = FALSE)
```


## Purpose

This tutorial was adapted from [Frank McCown's](https://sites.harding.edu/fmccown/r/) site on simple graphs in R. Once complete, students should be familiar with the **following learning objectives**:

* Learn to create different graphs using basic R functions
  + Line Graphs
  + Bar Graphs 
  + Pie Graphs
  + Histograms
  + Dot Graphs
* Learn to manipulate and customize graphs created with base R
* Apply rendering methods from *Week* videos to create a PDF of graphs

**Submission**

For lab assignment #8, use dataset #1 and dataset #2 to create graphs similar to those produced in this tutorial. Choose an appropriate subset of the data for the type of graph you are making. Use this week's lecture videos to render a PDF of plots from **ONE** dataset. Submit this PDF along with your response in a text file `LAST_NAME_Reflection9.txt` to the following reflection question on Canvas:

*You how important it is to use the correct type of graphic to accurately represent your data, but pie graphics typically have a poor reputation in the scientific community for most data. Why do you think that is? When do you think pie graphics can be useful?*

## Getting Started

This tutorial package was created in Rstudio using R markdown and integrated with an R shiny interface for an interactive experience.

The interactive code blocks behave just as they would in R. If you get stuck somewhere, use the solution/hint button for guidance!

If you have any questions, or find any issues, please let me know at adc0032@auburn.edu! 

*Here's a simple exercise with an empty code chunk provided for entering the answer.*

### Demo Exercise 

*Here's a simple demonstration with an empty code chunk provided for entering the answer.*

```{r two-plus-two, exercise=TRUE, exercise.lines = 2}

```

```{r two-plus-two-hint}
2+2
```

### Next Steps

Easy enough, right?! 

You will be using datasets borrowed from [Assignment #6](http://webhome.auburn.edu/~tds0009/WILD7150/Assignments/Assign6.html) in [Dr. Todd Steury's WILD 7150 course](http://webhome.auburn.edu/~tds0009/wild7150.html). This tutorial uses Dataset #3. Go back and use Datasets #1 and #2 with the commands you've used in this tutorial to produce similar plots. 

Here's a quick look at dataset #3. This dataset contains tree height at different ages for 16 individual trees. 

Modify the following code to limit the number of rows printed to 5:

```{r print-limit, exercise=TRUE, exercise.eval=TRUE}
agingtrees
```

```{r print-limit-hint}
head(agingtrees)
```

## Line Graphs

Let's say we are interested in looking at tree height for individual 5 at all ages in our data.





## Bar Graphs

Let's say we are interested in looking at tree height for all individuals in our data at age 14.

## Pie Graphs

## Histograms
How about we look at the distribution of heights 

## Dot Graphs

## Base Graph Customization

### Exercise with Hint

*Here's an exercise where the chunk is pre-evaulated via the `exercise.eval` option (so the user can see the default output we'd like them to customize). We also add a "hint" to the correct solution via the chunk immediate below labeled `print-limit-hint`.*



### Quiz

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```
