---
title: "Simple Graphs in R"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
description: >
  Learn how to produces different types of graphs with base R. This tutorial     was heavily insipired by Frank McCowns's site Producing Simple Graphs in with   R. The tutorial depends on the WILD7150 dataset, currently hosted on github. 
---

```{r setup, include=FALSE}
# Package for setup
library(devtools)
# Package for the Tutorial
library(learnr)
# Package of packages for manipulating datasets
library(tidyverse)
# Data Packaged
library(WILD7150)
# Index of color options in R
colpkr <- colors()
knitr::opts_chunk$set(echo = FALSE)
```

## Purpose

This tutorial was adapted from [Frank McCown's](https://sites.harding.edu/fmccown/r/) site on simple graphs in R. Once complete, students should be familiar with the **following learning objectives**:
 
* Learn to create different graphs using basic R functions
  + Line Graphs
  + Bar Graphs 
  + Pie Graphs
  + Histograms
  + Dot Graphs
* Learn to manipulate and customize graphs created with base R
* Apply rendering methods from *Week* videos to create a PDF of graphs

**Submission**

For lab assignment #8, use dataset #1 and dataset #2 to create graphs similar to those produced in this tutorial. Choose an appropriate subset of the data for the type of graph you are making. Use this week's lecture videos to render a PDF of plots from **ONE** dataset. Submit this PDF along with your response in a text file `LAST_NAME_Reflection9.txt` to the following reflection question on Canvas:

*You how important it is to use the correct type of graphic to accurately represent your data, but pie graphics typically have a poor reputation in the scientific community for most data. Why do you think that is? When do you think pie graphics can be useful?*

## Getting Started

This tutorial package was created in Rstudio using R markdown and integrated with an R shiny interface for an interactive experience.

This tutorial package is being shared with you in **source** format, which means that editing/moving files with disrupt functionality of the code. **If you have this issue, re-install the package from Github.**  

The interactive code blocks behave just as they would in R. If you get stuck somewhere, use the solution button for guidance!

If you have any questions, or find any issues, please let me know at adc0032@auburn.edu! 

*Here's a simple exercise with an empty code chunk provided for entering the answer.*

Write the R code required to add two plus two:

```{r two-plus-two, exercise=TRUE, exercise.lines = 1}

```

```{r two-plus-two-solution}
2+2
```

### Next Steps

Easy enough, right?! 

You will be using datasets borrowed from
[Dr. Todd Steury's WILD 7150 course](http://webhome.auburn.edu/~tds0009/wild7150.html) in a package I created called "WILD7150".  This tutorial uses `agingtrees` (dataset #3 from Dr. Steury's website). Go back and use `pickygrasshoppers` and `hormonaltrees` (datasets #1 and #2) with the commands you've used in this tutorial to produce similar plots. 

Here's a quick look at `agingtrees`.
This dataset contains tree height at different ages for 16 individual trees. 

Modify the following code to limit the number of rows printed to 5:

```{r print-limit, exercise=TRUE, exercise.eval=TRUE, exercise.lines = 1}
agingtrees
```
 
```{r print-limit-solution}
head(agingtrees)
```

## Line Graphs

### Subsetting

Let's say we are interested in looking at tree height for individual 5 at all ages in our data.

Modify the following code to subset "individual 5" data into vector `ind5`:

```{r subset-ind5, exercise=TRUE, exercise.eval=FALSE}
# Define the ind5 vector with a subset of the data for individual 5
# Within tidyverse are a multitude of packages, here we are using dplyr's filter function

ind5 agingtrees %>% filter(Individual == "")
ind5
```

```{r subset-ind5-solution}
ind5 <- agingtrees %>% filter(Individual == "5")
ind5
```

### Plotting

Nice! It looks like we've successfully filtered the dataset to only include data from individual 5 within the vector `ind5`

What about a plot? Run the code below to graph height with default settings:

```{r plot-subset-ind5, exercise=TRUE, exercise.eval=FALSE}
ind5 <- agingtrees %>% filter(Individual == "5")

# Graph of size values for individual 5
plot(ind5$Size)
```

Let's add a title and other details to the graph by personalizing the points with a color and overlaying a line

```{r plot2-subset-ind5, exercise=TRUE, exercise.eval=FALSE}
ind5 <- agingtrees %>% filter(Individual == "5")

# Graph of size values for individual 5 with customization
plot(ind5$Size, type = "o", col = "orange")

# Adding a title with customization
title(main = "Individual 5 Heights", col.main = "blue", font.main = 4)
```

### Height by Age

Realistically, we are not interested in looking at height alone, we are interested in height based on age. 

Use `~` to plot *height by age* :

```{r plot3-subset-ind5, exercise=TRUE, exercise.eval=FALSE, exercise.lines = 8}
ind5 <- agingtrees %>% filter(Individual == "5")

# Graph of size values for each age value for individual 5 with customization
plot(ind5$Size, type = "o", col = "orange")

# Adding a title with customization
title(main = "Tree ID 5 Heights for Age(YR) 10 to 20 ", col.main = "blue", font.main = 4)
```

```{r plot3-subset-ind5-solution}
ind5 <- agingtrees %>% filter(Individual == "5")
plot(ind5$Size~ind5$Age, type = "o", col = "orange")
title(main = "Tree ID 5 Heights for Age(YR) 10 to 20 ", col.main = "blue", font.main = 4)
```

*If you are wondering why it looks the same (except for the x axis), it is because the data is organized by increasing age, and therefore matches the index of values.*


### Adding A Tree

Let's add data from tree ID 2 to our graph:

```{r two-trees, exercise=TRUE, exercise.eval=FALSE, exercise.lines = 10}
ind5 <- agingtrees %>% filter(Individual == "5")
# Subset data for tree ID 2
ind2 <- 

plot(ind5$Size~ind5$Age, type = "o", col = "orange")
# Graph ind2 with grey lines and square points
lines(ind2$Size~ind2$Age, type="o", pch=22, lty=2, col="grey")

title(main = "Tree ID 5 Heights for Age(YR) 10 to 20 ", col.main = "blue", font.main = 4)
```

```{r two-trees-solution}
ind5 <- agingtrees %>% filter(Individual == "5")
ind2 <- agingtrees %>% filter(Individual == "2")

plot(ind5$Size~ind5$Age, type = "o", col = "orange")
lines(ind2$Size~ind2$Age, type="o", pch=22, lty=2, col="grey")
title(main = "Tree ID's 2 & 5 Heights for Age(YR) 10 to 20 ", col.main = "blue", font.main = 4)
```

### Adding more data and some PIZZAZZ!

These are base R graphs (and there is nothing wrong with that, hehe), but they need a bit of sprucing (editing colors, shapes, labels, legends, etc.). **See my comment on getting colors below!**

This time we are going to subset data from 3 trees, and update colors, shapes, and axis titles.

In the background for this upcoming chunk, I'm utilizing `tidyverse` packages to select height for three different trees and organizing them into a 
new data frame. To see how this was performed, **carefully** navigate to line 185 in the `simplegraphs.Rmd` file located in `inst/tutorials/SimpleRGraphs`

```{r fin-line-subset}
# vectoring data I am interested in, and making a new tibble (data frame)
ind2 <- agingtrees %>% filter(Individual == "2") %>% select(Size, Tree2 = Size)
ind5 <- agingtrees %>% filter(Individual == "5") %>% select(Size, Tree5 = Size)

# Here we are: piping agingtrees to filter by individual, selecting the size column and renaming the column
ind13 <- agingtrees %>% filter(Individual == "13") %>%
          select(Size, Tree13 = Size)

# Combining the three trees we want to plot into a single data frame santrees
santrees <- bind_cols(ind2, ind5, ind13)
```

Let's check out the new data frame called `santrees` that was created in the background, and use it to add some finishing touches to our plot

```{r final-plot,exercise=TRUE, exercise.eval=FALSE, exercise.lines = 20, exercise.setup = "fin-line-subset"}
# Check out santrees
head(santrees)

# Determine the largest y value in the dataset. Don't you hate when your axes are too short!?
mxy <- max(santrees)

# Let's make a vector holding colors for Tree 2, 5, and 13
# run colors() in your local rstudio console to check out the 657 options!
  # You can also run colpkr (I put colors() into an object with that name!) and call colors by   index
plotcols <- c("slategray2","seagreen2","orange1")

# Create a base graphic incorporating mxy, with no axes and labels
plot(santrees$Tree2, type = "o", col = plotcols[1], ylim = c(0,mxy), axes = FALSE, ann = FALSE)

# Create x-axis using Age 10 - 20; side 1 = x axis
axis(1, at=1:11, lab=c(10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20))

# Create y-axis, displaying tick marks at every 6th mark. 
  # 6*0:max_y is the same as c(0,6,12,18); side 2 is the y axis
axis(2, las=1, at=6*0:mxy)

# Put a box around the graph
box()

# Let's add Tree 5 and 13
lines(santrees$Tree5, type = "o", col = plotcols[2],
      pch=22,lty=2)

lines(santrees$Tree13, type = "o", col = plotcols[3],
      pch=23,lty=3)


# Finally, let's label the rest of the graph and add a legend
title(main = "Tree Heights Across 11 Years ", col.main = "navy", font.main = 4)
title(xlab = "Age(Years)", col.lab="navy")
title(ylab = "Height(Meters)", col.lab="navy")
legend("bottomright", names(santrees), col=plotcols, lty = 1:3)
```

This code accomplishes the same goal. 
Remove any unused objects, and use line 10 to ensure that data from the third tree is included in the graph:

```{r final-plot-2, exercise=TRUE, exercise.eval=FALSE, exercise.lines = 15, exercise.setup = "fin-line-subset"}
mxy <- max(santrees)
plotcols <- c("slategray2","seagreen2","orange1")
plot(santrees$Tree2, type = "l", col = plotcols[1], ylim = range(santrees), 
     xlab = "Age (Years)", ylab = "Height (Meters)", axes = FALSE, col.lab="navy",
     ann = TRUE, cex.lab = 1, lwd = 3)
axis(1, at=1:11, las=2, lab=c(10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20))
axis(2, las=1, at=8*0:mxy)
box()
lines(santrees$Tree5, type = "l", col = plotcols[2],lty=2, lwd = 3)
lines()
title(main = "Tree Heights Across 11 Years ", col.main = "navy", font.main = 4)
legend("bottomright", names(santrees), cex=0.8, col=plotcols, 
   lty=1:3, lwd=3, bty="n")
```

```{r final-plot-2-hint}

plotcols <- c("slategray2","seagreen2","orange1")
plot(santrees$Tree2, type = "l", col = plotcols[1], ylim = range(santrees), 
     xlab = "Age (Years)", ylab = "Height (Meters)", axes = FALSE, col.lab="navy",
     ann = TRUE, cex.lab = 1, lwd = 3)
axis(1, at=1:11, las=2, lab=c(10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20))
axis(2, las=1, at=8*0:mxy)
box()
lines(santrees$Tree5, type = "l", col = plotcols[2],lty=2, lwd = 3)
lines(santrees$Tree5, type = "l", col = plotcols[3],lty=3, lwd = 3)
title(main = "Tree Heights Across 11 Years ", col.main = "navy", font.main = 4)
legend("bottomright", names(santrees), cex=0.8, col=plotcols, 
   lty=1:3, lwd=3, bty="n")
```
## Bar Graphs

### Height for a Single Tree
```{r base-bar, exercise=TRUE, exercise.eval=FALSE}
ind5 <- agingtrees %>% filter(Individual == "5")

# Create a bar graph of the heights from Tree ID 5 
barplot(ind5$Size)
```

Use the `main` `xlab` and `ylab` functions to add important labels to the graph, and use `seq` to clean up `names.arg` and `density`:
```{r base-bar2, exercise=TRUE, exercise.eval=FALSE, exercise.setup = "fin-line-subset"}
# Cleaning up code, labeling axes, and titling graph
barplot(santrees$Tree5,
        names.arg=c(10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20), 
        border="blue", density=c(5,10,15,20,25,30,35,40,45,50,55))

```

```{r base-bar2-hint}
barplot(santrees$Tree5, main="Tree 5 Heights Across 11 Years", xlab="Age (Years)",  
   ylab="Height (Meters)", names.arg=c(seq(10,20,1)), 
   border="blue", density=c(seq(2,22,2)))

```

### Height by Year for Three Trees

Let's look at multiple trees with `santrees` we made in the previous section:

```{r bar-by-tree, exercise=TRUE, exercise.eval=FALSE}

# Converting santrees to a matrix, using beside=TRUE to prevent stacking, using rainbow color scales for bar fill
barplot(as.matrix(santrees), main="Trees", ylab= "Height (Meters)",
   beside=TRUE, col=rainbow(11))

# Place the legend at the top-left corner, filling with the rainbow color scales 
legend("topleft", c("10Y","11Y","12Y","13Y","14Y","15Y","16Y","17Y","18Y","19Y","20Y"), cex=0.6, 
    fill=rainbow(11))
```

### Height by Individual for Three Ages 

So far, we've grouped the data by individual tree. Let's group the data by ages of trees.  

As with `santrees`, I've gone ahead and made a data frame of tree sizes at three chosen ages (source lines 309-318) called `tresages`. 

```{r fin-bar-subset}
# vectoring data I am interested in, and making a new tibble (data frame)
yr12 <- agingtrees %>% filter(Age == "12") %>% select(Size, Yr12 = Size)
yr15 <- agingtrees %>% filter(Age == "15") %>% select(Size, Yr15 = Size)
yr19 <- agingtrees %>% filter(Age == "19") %>% select(Size, Yr19 = Size)


# Combining the three ages we want to plot into a single data frame tresages
tresages <- bind_cols(yr12, yr15, yr19)
```

Update the code below to ensure the *y-axis limits are appropriate for the data*, 
*remove the box around the legend with `bty`*, and *play around with the `ncol` variable in the legend assignment to eliminate any overlap* of legend information with bars. Finally, remember that *`barplot` requires that the data be in a vector or matrix*: 

```{r fin-bar-plot, exercise=TRUE, exercise.eval=FALSE, exercise.setup = "fin-bar-subset"}
# Checking out tresages 
head(tresages)

# Creating a plot for tresages, converting to matrix
barplot(tresages, main="Tree Height", ylab= "Height (Meters)",
   beside=TRUE, col=rainbow(16))

# Place the legend at the top-left corner with no frame, using rainbow colors
legend("topleft", ncol = 2,
       c("Tree1","Tree2","Tree3","Tree4","Tree5","Tree6","Tree7","Tree8",
         "Tree9","Tree10","Tree11", "Tree12", "Tree13", "Tree14", "Tree15", "Tree16"), 
       cex=0.6, fill=rainbow(16))
```

```{r fin-bar-plot-hint}
head(tresages)

barplot(as.matrix(tresages), main="Tree Height", ylab= "Height (Meters)",
   beside=TRUE, col=rainbow(16), ylim = c(0,max(sanages)))
legend("topleft", ncol = 4,
       c("Tree1","Tree2","Tree3","Tree4","Tree5","Tree6","Tree7","Tree8",
         "Tree9","Tree10","Tree11", "Tree12", "Tree13", "Tree14", "Tree15", "Tree16"), 
       cex=0.6, bty="n", fill=rainbow(16))
```

### Stacked Bars

We've looked at the data with single and grouped bars, let's try out a stacked bar graph.
See what happens when you set `beside` to `FALSE` or remove it: 

```{r stacked-bar, exercise=TRUE, exercise.eval=FALSE, exercise.setup = "fin-bar-subset"}
# Creating a plot for tresages, converting to matrix
barplot(as.matrix(tresages), main="Tree Height", ylab= "Height (Meters)",
   beside = TRUE, col=rainbow(16))

# Check out usage of paste command when you don't want to make long lists of names and such.
legend("topleft", ncol = 4,
       c(paste0("Tree", seq(1,16))), 
       cex=0.6, fill=rainbow(16))

```

Later in the tutorial, I will demonstrated adjusting the margins to make room to add the legend adjacent to the graph, so that we don't 
worry about our legend covering features of our graph.

While we are here, let's try a graph of `santrees` with horizontal bars (this way there will be space for the legend on the graph):
```{r horiz-bar,exercise=TRUE, exercise.eval=TRUE, exercise.setup = "fin-line-subset"}
# Creating a plot for tresages, converting to matrix
barplot(as.matrix(santrees), main="Tree Height", xlab= "Height (Meters)",
   horiz = TRUE, beside = FALSE, col=rainbow(16))

# Check out usage of paste command when you don't want to make long lists of names and such.
legend("bottomright", ncol = 4,
       c(paste0("Tree", seq(1,16))), 
       cex=0.6, fill=rainbow(16))
```

## Pie Graphs

Ahh! Good ole pie graph! I fondly remember these being my favorite in primary school, mainly because of the shape, haha. I've grown up and discovered that, often, we (hoomans) aren't that great at interpreting data in a circular format.

Check out this post on [Pie Caveats](https://www.data-to-viz.com/caveat/pie.html) on the site [from-Data-to-Viz](https://www.data-to-viz.com/)

### Subsetting & Base Graph

Let's build a pie graphic anyway:

```{r bad-pie, exercise=TRUE, exercise.eval=FALSE}
# Subset data for trees at age 15
age15 <- agingtrees %>% filter(Age == "15")

# Creating a pie graph of individual tree heights at age 15
pie(age15$Size)
```

### Adding Features

Add a title, labels, and colors to the pie graph:
```{r bad-pie-2, exercise=TRUE, exercise.eval=FALSE}
age15 <- agingtrees %>% filter(Age == "15")

pie(age15$Size, main = , 
    col = , labels = )
```

```{r bad-pie-2-hint}
age15 <- agingtrees %>% filter(Age == "15")

pie(age15$Size, main = "Tree Height at Age 15", 
    col = rainbow(length(age15$Individual)), labels = c(paste0("Tree", seq(1,16))))
```

### Percentages

Lastly, let's label the pie graph with percentages instead of tree IDs. 
Here you will see how to place the legend adjacent to the graphic. Play around with the X,Y coordinates on line 19: 

```{r bad-pie-3, exercise=TRUE, exercise.eval=TRUE, exercise.lines = 20 }

age15 <- agingtrees %>% filter(Age == "15")

# Using a grey scale, ideal for black & white print
colors <- c(grey.colors(16))

# Calculate the percentage for each tree height, round to 1 decimal place
age_labels <- round(age15$Size/sum(age15$Size) * 100, 1)

# Pasting '%' after each value
age_labels <- paste0(age_labels, "%")

# Create a pie chart with defined heading and custom colors
# and labels
pie(age15$Size, main="Tree Heights at Age 15", col=colors, labels=age_labels,
   cex=0.8)

# Create a legend to the right of the graph
  # Notice that I am not using positions in quotes (i.e., "topleft", "bottom"). What happens if you change x (the first number) to 2?
legend(1.2, 0.7, c(paste0("Tree", seq(1,16))), cex=0.6, 
   fill=colors, ncol = 2)

```


## Dot Graphs

[Dot plots](https://en.wikipedia.org/wiki/Dot_plot_(statistics)) are the some of the most simplistic ways to represent quantitative measurements, categorically. 

Typically, they work better for smaller amounts of data, but visually are easier to digest 
than bar and pie graphs - while retaining the same amount of information content.

### Subsetting and Transposing

```{r dot-subtrans, exercise=TRUE, exercise.eval=FALSE, exercise.setup = "fin-bar-subset"}
# Let's use the tresages subset from before; using t() to transpose the first 6 results from the data frame
ttres <- t(head(tresages))
```

### Dot Graph

Here's our graph! The labels are crowded or non-existent, and it's sort of bland (Yikes!).

```{r dot-graph, exercise=TRUE, exercise.eval=TRUE, exercise.setup = "fin-bar-subset"}
ttres <- t(head(tresages))
# Create Dot graph
dotchart(ttres)
```

### Adding some color

Recall I put all of the possible color options in base R into an object called `colpkr`, 
so let's call colors by index for this chunk. 
Add x-axis label, increase the size of the title, and change the circles to triangles:

```{r fin-dot-graph, exercise=TRUE, exercise.eval=FALSE, exercise.setup = "fin-bar-subset"}
ttres <- t(head(tresages))
dotchart(ttres, color=c(colpkr[511], colpkr[637], colpkr[493]),
   main="Dotchart for Trees", cex=0.6)
```

```{r fin-dot-graph-hint}
ttres <- t(head(tresages))
dotchart(ttres, color=c(colpkr[511], colpkr[637], colpkr[493]),
   main="Dotchart for Trees", cex=0.6,cex.main = 2, pch = 24 , xlab = "Heights (Meters)")
```

## Histograms
Histograms help you characterize distribution and normality of your data.

Histograms are among the first summaries created for a fresh dataset. 

### Basic Histograms with WILD7150 Data

Let's look at the distribution of heights for at a single age, using our `tresages` subset: 

```{r base-his, exercise=TRUE, exercise.eval=TRUE, exercise.setup = "fin-bar-subset"}
# Create a histogram
hist(tresages$Yr19)
```


How about a distribution of heights across 3 ages? Let's combine heights for all ages in the 
`tresages` subset and create a histogram, and format the features of the graph:

```{r cat-his, exercise=TRUE, exercise.eval=FALSE, exercise.setup = "fin-bar-subset"}
# Concatenate tresages
allyr <- c(tresages$Yr19, tresages$Yr15, tresages$Yr12)

# Histogram with Features (color, title, xlabs)
hist(allyr, col=colpkr[48], ylim=c(0,20), main = "Histogram of Heights for Ages 12,15,& 17",
     xlab = "Height (Meters)")
```

### Choosing Bins
Build on the previous graph, this time forcing each height into its own bin by setting `breaks` to the max height in the data (you also may want to adjust the `ylim` values):
```{r fin-his, exercise=TRUE, exercise.eval=FALSE, exercise.setup = "fin-bar-subset"}
allyr <- c(tresages$Yr19, tresages$Yr15, tresages$Yr12)

# Maximum Y value (height) of allyr
mxy <-max()

# Single bin histogram with horizontal y-axis labels
  # using object holding number of heights in data (mxy)
  # right=F means that the cells are right open intervals,
  # i.e. from [1 to 2], included values from 1 up until and including (1..1.98,1.99... & 2)
hist(allyr, col=heat.colors(mxy), breaks=, ylim=c(0,5), xlab = "Height (Meters)",
   xlim=c(0,mxy), right=F, main="Histogram of Heights for Ages 12,15,& 17", las=1)

```

```{r fin-his-hint}
allyr <- c(tresages$Yr19, tresages$Yr15, tresages$Yr12)
mxy <-max(allyr)

# Single bin histogram with horizontal y-axis labels
  # using object holding number of heights in data (mxy)
  # right=F means that the cells are right open intervals,
  # i.e. from [1 to 2], included values from 1 up until and including (1..1.98,1.99... & 2)
hist(allyr, col=heat.colors(mxy), breaks=mxy, ylim=c(0,20), xlab = "Height (Meters)",
   xlim=c(0,mxy), right=F, main="Histogram of Heights for Ages 12,15,& 17", las=1)

```

### Histograms from Randomized Data

Plotting the [log(normal distribution)](https://en.wikipedia.org/wiki/Log-normal_distribution) 
for 10000 random numbers

```{r loghis, exercise=TRUE, exercise.eval=TRUE}
# Using AU zipcode as seed for random number generator
set.seed(36849)
# Getting 10,000 random numbers with a log-normal distribution
dstr <- rlnorm(10000)
hist(dstr)
```


```{r lognorm, exercise=TRUE, exercise.eval=TRUE}
# Get a random log-normal distribution
dstr <- rlnorm(10000)

# Calculate distribution, but don't plot (plot=FALSE) 
  # Using really small breaks (by 0.1)
hst <- hist(dstr, plot=FALSE, breaks=c(seq(0,max(dstr)+1, .1)))

# Using log="xy" to log transform both axes
plot(hst$counts, log="xy", pch=18, col=colpkr[459],
	main="Log-normal distribution",
	xlab="Value", ylab="Frequency")
```

## Other Base Graph Customization

Use this chart to add details to your base R graphs!

```{r misc-code, exercise=TRUE, exercise.eval=TRUE, exercise.lines = 25}
# Make an empty chart
plot(1, 1, xlim=c(1,5.5), ylim=c(0,10), type="n", ann=FALSE)

# Plot digits 0-4 with increasing size and color
text(1:5, rep(8.5,5), labels=c(0:4), cex=1:5, col=1:5)

# Plot symbols 0-4 with increasing size and color
points(1:5, rep(6,5), cex=1:5, col=1:5, pch=0:4)
text((1:5)+0.4, rep(6,5), cex=0.6, (0:4))

# Plot symbols 5-9 with labels
points(1:5, rep(4.5,5), cex=2, pch=(5:9))
text((1:5)+0.4, rep(4.5,5), cex=0.6, (5:9))

# Plot symbols 10-14 with labels
points(1:5, rep(3,5), cex=2, pch=(10:14))
text((1:5)+0.4, rep(3,5), cex=0.6, (10:14))

# Plot symbols 15-19 with labels
points(1:5, rep(1.7,5), cex=2, pch=(15:19))
text((1:5)+0.4, rep(1.7,5), cex=0.6, (15:19))

# Plot symbols 20-25 with labels
points((1:6)*0.8+0.2, rep(0.7,6), cex=2, pch=(20:25))
text((1:6)*0.8+0.5, rep(0.7,6), cex=0.6, (20:25))
```


### END

*You have completed the Simple Graphs in R tutorial! Happy Plotting!!*

After a quick quiz below, return to the **Purpose** tab and try out your new skills for your lab submission. 

Some questions to check your understanding of some concepts introduced in this tutorial package:

```{r quiz, echo=FALSE}
quiz(
  question("Which package used in this tutorial can help you manipulate and parse data?",
    answer("MASS"),
    answer("ggplot2"),
    answer("tidyverse", correct = TRUE),
    answer("codetools"),
    allow_retry = TRUE
  ),
  question("Which of the functions listed below are used to format and customize plots in base R?[select all that apply]",
    answer("text", correct = TRUE),
    answer("mean"),
    answer("geom_point"),
    answer("line", correct = TRUE),
    allow_retry = TRUE
  ),
  question("Which argument listed below forces barplot to group bars and not stack them?",
    answer("beside", correct = TRUE),
    answer("right"),
    answer("fill"),
    answer("main"),
    allow_retry = TRUE
  ),
  question("What function returns the maximum value of the object santrees?",
    answer("hist(santrees)"),
    answer("library(santrees)"),
    answer("sd(santrees)"),
    answer("max(santrees)", correct = TRUE),
    allow_retry = TRUE
  )
)
```
